---
title: "Pseudo-Random Password Generator"
author: "Christian Aeschbacher"
date: "10/15/2021"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Software: <br> Pseudo-Random Password Generator in Six Steps

## **CREDIT**: <br> Tech Know How ([YouTube Channel Link](https://www.youtube.com/channel/UCwgcmcn_iifLGs_38JIF6kw)) <br> *"How To Create A Strong Password Generator In R!"* <br> Jun 20, 2020 ([YouTube Video Link](https://www.youtube.com/watch?v=CM-sKNebC0o))

### Step One: <br> Create a "passWord" function
```{r pwFunction}
set.seed(1471) # for reproducibility

passWord <- function(LENGHT) {
  symbolsA <- c("+", "*", "%", "&", "/", "(", ")", "=", 
                "@", "#", "?", "'", "^", "!", "$", "?", 
                "-", "_", ".", ":", ",", ";", "<", ">")
  symbolsB <- c("?", "?", "?", "?", "|", "?", "?", "`", 
                "~", "?", "[", "]", "{", "}") 
  # less common symbols -> but could be a list of anything
  numbers10 <- c(0:9)
  pwChars <- c(letters, LETTERS, symbolsA, symbolsB, numbers10)
  # setting probabilities for each element of pwChars
  probabilities <- c(rep(0.40, 26), rep(0.20, 26), rep(0.10, 24), 
                     rep(0.10, 14), rep(0.20, 10)) 
  # can be easily modified/ adjusted
  pWord <- paste0(sample(pwChars, size = LENGHT, 
                         replace = TRUE, prob = probabilities
                         #, useHash : 
                         # logical indicating if the hash-version of the algorithm
                         # should be used. Can only be used for replace = FALSE, 
                         # prob = NULL, and size <= n/2, 
                         # and really should be used for large n, 
                         #as useHash=FALSE will use memory proportional to n.
                         ), collapse = "")
  return(pWord)
}
```

### Step Two: <br> Set desired password length and number of passwords 
```{r pwSettings}
pwLenght <- 10 # can be easily modified/ adjusted
pwNumber <- 1000 # can be easily modified/ adjusted
```

### Step Three: <br> Create a list based on pwNumber
```{r}
xy <- vector("list", pwNumber)
```

### Step Four: <br> Create a for-loop that calls the "passWord" function from Step One
```{r}
counter <- pwNumber
for (pwNumber in 1:pwNumber) {
  dfPassword <- passWord(pwLenght)
  xy[(pwNumber)] <- dfPassword
  counter <- counter-1
  #print(dfPassword)
}
```

### Step Five: <br> Place in dataframe and rename column to "Passwords"
```{r}
dfPw <- data.frame(matrix(unlist(xy), ncol = 10,
                          byrow = TRUE), stringsAsFactors = FALSE)
colnames(dfPw) <- c("Passwords 1-100", "Passwords 101-200", 
                    "Passwords 201-300", "Passwords 301-400", 
                    "Passwords 401-500", "Passwords 501-600", 
                    "Passwords 601-700", "Passwords 701-800", 
                    "Passwords 801-900", "Passwords 901-1000")
```

### Step Six: <br> Write the dataframe to a text file
```{r}
write.table(dfPw, "PasswordFile.txt", sep = "\t")
```

# Et Voilà!







